This dissertation would not have been possible without the support 
of numerous people, as this dissertation embodies the phrase 
``it takes a village''. I would first like to thank my PhD advisor and 
committee chair, Dr. 
Madicken Munk. You helped me in many capacities, including technical 
mentorship, time management, and professional development opportunities 
to help prepare me for the next stages of my career. Without you, my PhD 
experience would not have been as enriching and rewarding. I would also like 
to thank my committee members: Prof. Jim Stubbins, Prof. Tomasz Kozlowski, 
Prof. John Abelson, and Dr. Bo Feng for their time and guidance on my dissertation. 

In addition to those on my committee, I received substantial mentorship from 
many others. I am grateful to Dr. Scott Richards for his mentorship while I 
was at Argonne National Lab. Without him, I would have been in graduate school 
for twice as long. I am also grateful for the other members of the 
Reactors and Fuel Cycle Analysis (RFCA) group members, Drs. Kalin
Kiesling, Tingzhou Fei, Yan Cao, Roger Blomquist, and Hansol Park, 
for their mentorship, support, and for being wonderful colleagues during my 
time at Argonne National Lab. 

I am also grateful to the \Cyclus community, namely Prof. 
Paul P.H. Wilson, Dr. Baptiste Mouginot, and Jin Whan Bae, for their warm 
welcome to the \Cyclus community and their support in helping me learn about 
fuel cycle simulators. I would also like to thank the OpenMC community 
for their help and guidance in learning about OpenMC. 
Additionally, I am eternally grateful to Prof. 
Kathryn Huff, with whom I began my PhD journey. You helped me sculpt my 
dissertation and pushed me to learn new skills and explore new things. 
I would not be the researcher I am if I didn't have your initial 
guidance. 

I am incredibly thankful to all of the members of the \gls{ARFC} Research 
group for all of their guidance, support, and friendship -- Gwendolyn 
Chee, 
Nathan Ryan, Sam Dotson, Sun Myung Park, Zo\"{e} Richter, Luke Seifert, 
Olek Yardas, Roberto Fairhurst-Agosta, Nataly Panczyk, Lu Kissinger, 
Nicholas Yeung, Ceser Zambrano, Nathan Glaser, and Elijah Capps. 
A special thank you to Nathan Ryan, Nataly Panczyk, Ceser Zambrano, 
and Nathan Glaser for their proof-reading of this document and the 
others I wrote during my 
time in \gls{ARFC}. I would also like to acknowledge and thank all of the other 
UIUC NPRE students and communities that were part of my journey, as 
you all made grad school much more bearable, especially as we went through 
the COVID-19 pandemic. Furthermore, to my friends across the country that 
supported me through graduate school, I am forever grateful to you. 

Fianlly, I would like to thank my family, Kyle Anderson, and Little R
for the love and support each of you gave me throughout my journey. 

This material is based upon work supported under an Integrated University 
Program Graduate Fellowship. Any opinions, findings, conclusions or 
recommendations expressed in this publication are those of the author(s) 
and do not necessarily reflect the views of the Department of Energy Office 
of Nuclear Energy. This work was also partially funded through a SURGE 
Fellowship from the Grainger College of Engineering at the University of 
Illinois Urbana-Champaign.